Towards Cloud Bursting for Extreme Scale Supercomputers\\ (Unrefereed Workshop Manuscript)

### 2014-07-01 paper/src/1_introduction.tex
0701

\section{Introduction}
\label{sec:introduction}
Supercomputers provide an increasing number of scientific applications with high computational power by a large number of processors, large bandwidth memory and interconnects.
%Data size need to be processed grows rapidly these days, which is known as Big Data, people perfer to use supercomputer to analyze Big Data for it supports high parallelism.
%Multi-user can use supercomputer at the same by using batch queue system which manage nodes and job submission.
%Although supercomputers can offer the high computational power, there are several situations where a supercomputer can not satisfy user's demands even there are still some idle nodes, consider there are 50 nodes available, a user submit a serial application use only one node for an hour, after that, a job using 50 nodes is submitted, and have to wait until previous job finished although there are 49 nodes remainning available.
%high parallel application runs faster on Supercomputer for fully usage of computing resource, but a serial application will occupy computing nodes for a long time causing other application must wait.
Although supercomputers can also offer high computational capacity, the computational resources are not unlimited. 
Supercomputers can not meet the demands of users when the demands exceed the limit. 
For example, on grand challnge projects, computational resources are exclusively used for the scientific discoveries~\cite{Scientific_Grand_Challenges_Crosscutting_Technologies_for_Computing_at_the_Exascale, Scientific_Grand_Challenges_in_National_Security_the_Role_of_Computing_at_the_Extreme_Scale}, and the system can not provide adequate resources for other jobs.
In addition, under power badget constrain~\cite{Exploring_Hardware_Overprovisioning_in_Power-constrained_High_Performance_Computing,Operation_of_TSUBAME_2_0_Green_Supercomputer_dealing_with_Power_Crisis}, a part of compute nodes are required to be shutdown to reduce its power consumption, which also leads inadequate of resources for all users.

One of solutions to provide adequate computational resources under the constrains, is federating the supercomputer with public clouds.
By moving a part of jobs to public clouds when there are not enough
compute nodes available, we can meet the needs for users' requests even under the constrains, which is known as \emph{cloud bursting}~\cite{Optimizing_Service_Level_Agreements_for_Autonomic_Cloud_Bursting_Schedulers, A_Framework_for_Data-Intensive_Computing_with_Cloud_Bursting}.
Although cloud bursting is technically feasible~\cite{Eucalyptus,stratos,Seagull}, 
and is employed by several private companies, there are several problems if we apply the techniqu to supercomputers.
One of the problems is a significant performance gap between supercomputers and public clouds especially in I/O performance
%there will still be several problems when we try to federate a supercomputer with a public cloud, 
%and there are several studies on cloud burst about cost\cite{Seagull}, execution time\cite{time_and_cost}, etc..
%Especially, low I/O performance between supercomputers and public clouds is critical.
%The biggest problem will be data transfer throughput between two environment, 
For example, if we migrate a part of jobs from a supercomputer to a public cloud or run jobs on a public cloud insted of a supercomputer, and the jobs need data located in a parallel file system (PFS), the data need to be transfered between the two system.
% supercomputers usual deal with Gigabyte or even Petabyte input and output of data, 
Because the two systems are usually geographically distributed, and network throghput between the systems is quite low,
the low I/O throughput suffers supercomputer users. Thus, improving I/O throughputs between two systems, which are geographically distributed each other, is ciritical in federating supercomputers with public clouds

In this paper, we propose I/O burst buffers. The I/O burst buffers consists of I/O dedicated staging nodes, which cache hot files in the buffers, and enables asynchronous write back for improving both read and write operations to remote file systems.
We also model the I/O burst buffers to optimize  configurations of the I/O burst buffers according to dynamically changing environments
\kento{Do you think this sentence is resonable to describe your model ?}.
According to our simulation, we can achieve a 4-20 times higher throughput (depends on data locality and other factors) by using 20 I/O buffer nodes on Amazon EC2 environment, as well sa reduce 2-12 times of cost.
\kento{please summirize the evaluation resutls here.}
%  architecture that uses multiple nodes in each system as an I/O nodes 
%to improve I/O throughput concurrent data transferring, and an I/O burst buffer model 
%that uses to switch between I/O burst buffer mode and direct connect mode.
%This I/O bursting buffer architecture can be mainly used two situation, first in data I/O, the other one will be when there are some nodes need to migrate from a cloud to another cloud with snapshot, snapshots can be transferred without be stored to shared storage.
%Since, I/O bursting buffer needs three times data transfer, sometimes direct transfer will achieve a higher throughput, I/O bursting buffer model using a evaluation throughput using I/O bursting buffer and without I/O bursting buffer to determine I/O bursting buffer mode or direct connection mode.
%Also, public cloud usually charges for nodes usage, I/O bursting buffers may reduce the computation time, 
%but I/O nodes will be charged for money, we also provide a cost-based model, to reduce the overall cost.

Our contributions can be summrized as following:
\begin{itemize}
	\item A I/O burst buffer for increasing data transfer throughput between two systems;
	\item A throughput-based I/O burst buffer model, which estimate I/O throughput of systems with I/O burst buffers, and a cost-based I/O burst buffer model, which estimate overall cost give a system configuration;
        \item Evaluation of the I/O burst buffer architecture based the performance models by using real data obtained from several benchmarks from the TSUBAME supercomputer and AMAZON EC2.
\end{itemize}
%2
The rest of this paper is organized as follows. 
In Section \ref{sec:motivation}, we clarify the motivation and the background.
We introduce an overview of the I/O bursting buffer architecture in Section \ref{sec:burst_buffer}, 
and show the performance models to evaluate the I/O bursting buffer architecture in Section \ref{sec:model}. 
In Section \ref{sec:evaluation}, we present our experimental results based of our perfomrance models. %based on data obtained from several benchmark on TSUBAME V queue and AMAZON EC2 
Finally, we detail related work in Section \ref{sec:related_work}, and conclusion in Section \ref{sec:conclusion}.

>>>>

\section{Introduction}
\label{sec:introduction}
Supercomputers provide an increasing number of scientific applications with high computational power by a large number of processors, large bandwidth memory and interconnects.
%Data size need to be processed grows rapidly these days, which is known as Big Data, people perfer to use supercomputer to analyze Big Data for it supports high parallelism.
%Multi-user can use supercomputer at the same by using batch queue system which manage nodes and job submission.
%Although supercomputers can offer the high computational power, there are several situations where a supercomputer can not satisfy user's demands even there are still some idle nodes, consider there are 50 nodes available, a user submit a serial application use only one node for an hour, after that, a job using 50 nodes is submitted, and have to wait until previous job finished although there are 49 nodes remainning available.
%high parallel application runs faster on Supercomputer for fully usage of computing resource, but a serial application will occupy computing nodes for a long time causing other application must wait.
Although supercomputers can also offer high computational capacity, the computational resources are not unlimited. 
Supercomputers can not meet the demands of users when the demands exceed the limit. 
For example, on grand challenge projects, computational resources are exclusively used for the scientific discoveries~\cite{Scientific_Grand_Challenges_Crosscutting_Technologies_for_Computing_at_the_Exascale, Scientific_Grand_Challenges_in_National_Security_the_Role_of_Computing_at_the_Extreme_Scale}, and the system can not provide adequate resources for other jobs.
In addition, under power budget constrain~\cite{Exploring_Hardware_Overprovisioning_in_Power-constrained_High_Performance_Computing,Operation_of_TSUBAME_2_0_Green_Supercomputer_dealing_with_Power_Crisis}, a part of compute nodes are required to be shutdown to reduce its power consumption, which also leads inadequate of resources for all users.

One of solutions to provide adequate computational resources under the constrains, is federating the supercomputer with public clouds.
By moving a part of jobs to public clouds when there are not enough
compute nodes available, we can meet the needs for users' requests even under the constrains, which is known as \emph{cloud bursting}~\cite{Optimizing_Service_Level_Agreements_for_Autonomic_Cloud_Bursting_Schedulers, A_Framework_for_Data-Intensive_Computing_with_Cloud_Bursting}.
Although cloud bursting is technically feasible~\cite{Eucalyptus,stratos,Seagull}, 
and is employed by several private companies, there are several problems if we apply this technique to supercomputers.
One of the problems is a significant performance gap between supercomputers and public clouds especially in I/O performance
%there will still be several problems when we try to federate a supercomputer with a public cloud, 
%and there are several studies on cloud burst about cost\cite{Seagull}, execution time\cite{time_and_cost}, etc..
%Especially, low I/O performance between supercomputers and public clouds is critical.
%The biggest problem will be data transfer throughput between two environment, 
For example, if we migrate a part of jobs from a supercomputer to a public cloud or run jobs on a public cloud insted of a supercomputer, and the jobs need data located in a parallel file system (PFS), the data need to be transferred between the two system.
% supercomputers usual deal with Gigabyte or even Petabyte input and output of data, 
Because the two systems are usually geographically distributed, and network throughput between the systems is quite low,
the low I/O throughput suffers supercomputer users. Thus, improving I/O throughput between two systems, which are geographically distributed each other, is critical in federating supercomputers with public clouds.

In this paper, we propose I/O burst buffer architecture. The I/O burst buffers consists of I/O dedicated staging nodes, which cache hot files in the buffers, and enables asynchronous write back for improving both read and write operations to remote file systems.
We also model the I/O burst buffers to optimize  configurations of the I/O burst buffers according to dynamically changing environments
%\kento{Do you think this sentence is resonable to describe your model ?}.
According to our simulation, we can achieve a 4-20 times higher throughput (depends on data locality and other factors) by using 20 I/O buffer nodes on Amazon EC2 environment, as well as reduce 2-12 times of cost.
%\kento{please summirize the evaluation resutls here.}
%  architecture that uses multiple nodes in each system as an I/O nodes 
%to improve I/O throughput concurrent data transferring, and an I/O burst buffer model 
%that uses to switch between I/O burst buffer mode and direct connect mode.
%This I/O bursting buffer architecture can be mainly used two situation, first in data I/O, the other one will be when there are some nodes need to migrate from a cloud to another cloud with snapshot, snapshots can be transferred without be stored to shared storage.
%Since, I/O bursting buffer needs three times data transfer, sometimes direct transfer will achieve a higher throughput, I/O bursting buffer model using a evaluation throughput using I/O bursting buffer and without I/O bursting buffer to determine I/O bursting buffer mode or direct connection mode.
%Also, public cloud usually charges for nodes usage, I/O bursting buffers may reduce the computation time, 
%but I/O nodes will be charged for money, we also provide a cost-based model, to reduce the overall cost.

Our contributions can be summarized as following:
\begin{itemize}
	\item A I/O burst buffer architecture for increasing data transfer throughput between two systems;
	\item A throughput-based I/O burst buffer model, which estimate I/O throughput of systems with I/O burst buffers, and a cost-based I/O burst buffer model, which estimate overall cost give a system configuration;
        \item Evaluation of the I/O burst buffer architecture based the performance models by using real data obtained from several benchmarks from the TSUBAME supercomputer and Amazon EC2.
\end{itemize}
%2
The rest of this paper is organized as follows. 
In Section \ref{sec:motivation}, we clarify the motivation and the background.
We introduce an overview of the I/O bursting buffer architecture in Section \ref{sec:burst_buffer}, 
and show the performance models to evaluate the I/O bursting buffer architecture in Section \ref{sec:model}. 
In Section \ref{sec:evaluation}, we present our experimental results based of our performance models. %based on data obtained from several benchmark on TSUBAME V queue and Amazon EC2 
Finally, we detail related work in Section \ref{sec:related_work}, and conclusion in Section \ref{sec:conclusion}.

### 2014-07-01 paper/src/4_model.tex
0701

\section{I/O Burst Buffer Model}
\label{sec:model}
\kento{First, again mention why the modeling is important for reminder}
%\begin{figure}[tb]
%	\centering
%	\includegraphics
%	\caption{definition}
%	\label{definition}
%\end{figure}

Since the instance type choice, Ethernet condition, Internet condition will affect the actual I/O throughput between two system, we introduce a throughput-based model, cost-based model and buffer queue write back model used to predict throughput, overall cost and in buffer rate when use I/O burst buffer and direct I/O, and using these predict model to make decision like which type of instance should use, and how many I/O nodes is needed in a particular cases.
\kento{this sentences should be in the previsou section}.

@@

\subsection{Throughput-based Model}
%There are many facts will affect throughput of Internet, so here a moniter is used to evaluate throughput between 
First we consider direct I/O, computing nodes read from and write back to storage in another system directly.
In the case of direct I/O \kento{What is direct I/O. I think it means direct connection mode in Section 3, but no explanation at all}, computing nodes connect to storage in another system directly, there is only one data transfer, so both read and write throughput \kento{read ? or write ? or both ?} will be:%there are two data transfers: computation nodes to I/O buffer nodes in system 2, I/O buffer nodes in system 2 to storage in system 1, so throughput will be:
\begin{equation}
	\text{thr}_{\text{direct}}=D_1(c_2) \label{throughput1}
\end{equation}

When using I/O burst buffer, there will be three data transfers: computation nodes to I/O buffer nodes in system 2, I/O buffer nodes in system 2 to I/O buffer nodes in system 1, I/O buffer nodes in system 1 to storage in system 1, 
for reading, if required file is buffered in buffer queue, computing node can read data from buffer queue directly, then throughput will be:$E_2(n_2)$, similiarly, if buffer queue still have enough space for I/O data when issue a write request, computing nodes can write data to buffer queue, and throughput also will be:$E_2(n_2)$.

If required file is not buffered in buffer queue when issue a read request, or when issue a write request buffer queue is full, the throughput will be:$\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)$, since for read request, file need to be read from storage in another system Internet, and for write request, it need to wait until buffer buffer write buffered file back the storage.
throughput \kento{write ? and read ?. Explain how the buffer queue works (1) if buffer space is avaialble for write, (2) reading data is in the buffer queue. We need expian this in both previous section and in here} here we summary them as:
\begin{eqnarray}
	\text{thr}_{\text{I/O buffer}}=\begin{cases}
		E_2(n_2) &\text{buffer queue available}\\ 
	\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\} &\text{buffer queue full or file miss}
	\end{cases} \label{throughput2}
\end{eqnarray}
Although we have two cases for each read and write request (in buffer or not in buffer), it is very difficult to predict the in buffer rate, since it will be affected by I/O size, Internet throughput, buffer queue size and so on.
\kento{Why do you swithches between direct I/O and burst buffer?}
%\begin{equation}
%	\begin{cases}
%		\text{thr}_{\text{direct}} \geq \text{thr}_{\text{I/O buffer}} & \text{use direct I/O}\\
%		\text{thr}_{\text{direct}} < \text{thr}_{\text{I/O buffer}} & \text{use I/O burst buffer}
%	\end{cases}
%\end{equation}

\kento{Mention how do you switch between I/O burst buffers and direct I/O. Will you dynamically shutdown/boot burst buffer nodes on demain ?. If so, please explain so, but there is a time lag before shutdown/boot are completed. So say somthing like "We will solve the problem in future work'' or else}

\subsection{Cost-based Model}
\kento{Again, it's hard to understand due to lack of information. Please read carfully over and over again and add more explanation like in the above}
Although we may use I/O burst buffer to achieve a high I/O throughput and leading a decrease of execution time, and according to public cloud pay for usage policy, the cost for computing nodes may reduce, the relation between overall cost and I/O throughput can not be such simple, since I/O nodes will still charged for usage, and if we use a instance with high Ethernet condition in order to get a higher throughput, we may be charged for more money.

@@

here we compute cost by using $T_1,T_2,T_3$:
\begin{equation}
	\text{cost}_\text{direct}=c_2\times C_2M(T_1)+n_2\times C_2HM(T_1)
\end{equation}
\kento{According to the difinition of $C_i\_Money(T)$ and $T_i$, the above model seems to be wrong. Please read carfully the model is correct}
\begin{align}
	\begin{cases}
		c_2\times C_2M(T_2)+n_1\times C_1HM(T_2)+n_2\times C_2HM(T_2)&\text{buffer queue available}\\
		c_2\times C_2M(T_3)+n_1\times C_1HM(T_3)+n_2\times C_2HM(T_3) &\text{buffer queue full}
	\end{cases}
\end{align}

@@

\kento{I'm workding if the throuput is 	$\text{thr}_{\text{direct}} < \text{thr}_{\text{I/O buffer}}$ the cost is $\text{cost}_{\text{direct}} \geq \text{cost}_{\text{I/O buffer}}$, which do you use, direct I/O and I/O buffer.}

@@

If the buffer size is unlimited. then we can buffer all data in the I/O buffer nodes, and achieve a high throughput in cloud burst \kento{Good work !! As I said in the different sections, it's important to remind its motivation before describing the algorithm, techniques, model, or methods for its reminder}.
However buffer size can not be unlimited, we can not buffer all data in the I/O buffer nodes, data in buffer nodes have to be write back to storage in another system.
The problem is which data should be written back to storage, like cache in cpu, if we can reduce cache miss in this situation, we can increase throughput. 
According to data locality, we use a priority queue to determine which data should be write back.

Consider Fig.~\ref{buffer queue}, assume average incoming throughput is A MB/s and average outgoing throughput is B MB/s, if A always larger than B, after $T$ time buffer queue will full.
\[T=\frac{m_2\times n_2}{A-B}\]

After that, since buffer queue is full, I/O server can not send more data to I/O buffer nodes, have to block any read and write request since that.
\kento{Why ??}.

>>>>

\section{I/O Burst Buffer Model}
\label{sec:model}
%\kento{First, again mention why the modeling is important for reminder}
%\begin{figure}[tb]
%	\centering
%	\includegraphics
%	\caption{definition}
%	\label{definition}
%\end{figure}

Since the instance type choice, interconnection network condition, Internet condition will affect the actual I/O throughput between two system, we introduce a throughput-based model, cost-based model and buffer queue write back model used to predict throughput, overall cost and in buffer rate when use I/O burst buffer and direct I/O, and using these predict model to make decision like which type of instance should use, and how many I/O nodes is needed in a particular cases.
%\kento{this sentences should be in the previsou section}.

@@

\subsection{Throughput-based Model}
%There are many facts will affect throughput of Internet, so here a moniter is used to evaluate throughput between 
First we consider direct I/O, computing nodes read from and write back to storage in another system directly.
In the case of direct I/O, computing nodes connect to storage in another system directly, there is only one data transfer, so both read and write throughput will be:%there are two data transfers: computation nodes to I/O buffer nodes in system 2, I/O buffer nodes in system 2 to storage in system 1, so throughput will be:
\begin{equation}
	\text{thr}_{\text{direct}}=D_1(c_2) \label{throughput1}
\end{equation}

When using I/O burst buffer, there will be three data transfers: computation nodes to I/O buffer nodes in system 2, I/O buffer nodes in system 2 to I/O buffer nodes in system 1, I/O buffer nodes in system 1 to storage in system 1, 
for reading, if required file is buffered in buffer queue, computing node can read data from buffer queue directly, then throughput will be:$E_2(n_2)$, similarly, if buffer queue still have enough space for I/O data when issue a write request, computing nodes can write data to buffer queue, and throughput also will be:$E_2(n_2)$.

If required file is not buffered in buffer queue when issue a read request, or when issue a write request buffer queue is full, the throughput will be:$\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)$, since for read request, file need to be read from storage in another system Internet, and for write request, it need to wait until buffer buffer write buffered file back the storage.
throughput% \kento{write ? and read ?. Explain how the buffer queue works (1) if buffer space is avaialble for write, (2) reading data is in the buffer queue. We need expian this in both previous section and in here} here we summary them as:
\begin{eqnarray}
	\text{thr}_{\text{I/O buffer}}=\begin{cases}
		E_2(n_2)&\\
		\text{buffer queue available}&\\ 
		\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\}& \\
		\text{buffer queue full or file miss}&
	\end{cases} \label{throughput2}
\end{eqnarray}
Although we have two cases for each read and write request (in buffer or not in buffer), it is very difficult to predict the in buffer rate, since it will be affected by I/O size, Internet throughput, buffer queue size and so on.
%\kento{Why do you swithches between direct I/O and burst buffer?}
%\begin{equation}
%	\begin{cases}
%		\text{thr}_{\text{direct}} \geq \text{thr}_{\text{I/O buffer}} & \text{use direct I/O}\\
%		\text{thr}_{\text{direct}} < \text{thr}_{\text{I/O buffer}} & \text{use I/O burst buffer}
%	\end{cases}
%\end{equation}

%\kento{Mention how do you switch between I/O burst buffers and direct I/O. Will you dynamically shutdown/boot burst buffer nodes on demain ?. If so, please explain so, but there is a time lag before shutdown/boot are completed. So say somthing like "We will solve the problem in future work'' or else}

\subsection{Cost-based Model}
%\kento{Again, it's hard to understand due to lack of information. Please read carfully over and over again and add more explanation like in the above}
Although we may use I/O burst buffer to achieve a high I/O throughput and leading a decrease of execution time, and according to public cloud pay for usage policy, the cost for computing nodes may reduce, the relation between overall cost and I/O throughput can not be such simple, since I/O nodes will still charged for usage, and if we use a instance with high interconnection network condition in order to get a higher throughput, we may be charged for more money.

@@

here we compute cost by using $T_1,T_2,T_3$:
\begin{equation}
	\text{cost}_\text{direct}=c_2\times C_2M(T_1)+n_2\times C_2HM(T_1)
\end{equation}
%\kento{According to the difinition of $C_i\_Money(T)$ and $T_i$, the above model seems to be wrong. Please read carfully the model is correct}
\begin{align}
	\begin{cases}
		c_2\times C_2M(T_2)+n_1\times C_1HM(T_2)+n_2\times C_2HM(T_2)&\\
		\text{buffer queue available}&\\
		c_2\times C_2M(T_3)+n_1\times C_1HM(T_3)+n_2\times C_2HM(T_3)&\\
		\text{buffer queue full}&
	\end{cases}
\end{align}

@@

%\kento{I'm workding if the throuput is 	$\text{thr}_{\text{direct}} < \text{thr}_{\text{I/O buffer}}$ the cost is $\text{cost}_{\text{direct}} \geq \text{cost}_{\text{I/O buffer}}$, which do you use, direct I/O and I/O buffer.}

@@

If the buffer size is unlimited. then we can buffer all data in the I/O buffer nodes, and achieve a high throughput in cloud burst% \kento{Good work !! As I said in the different sections, it's important to remind its motivation before describing the algorithm, techniques, model, or methods for its reminder}.
However buffer size can not be unlimited, we can not buffer all data in the I/O buffer nodes, data in buffer nodes have to be write back to storage in another system.
The problem is which data should be written back to storage, like cache in cpu, if we can reduce cache miss in this situation, we can increase throughput. 
According to data locality, we use a priority queue to determine which data should be write back.

Consider Fig.~\ref{buffer queue}, assume average incoming throughput is A MB/s and average outgoing throughput is B MB/s, if A always larger than B, after $T$ time buffer queue will full.
\begin{equation}
T=\frac{m_2\times n_2}{A-B}
\end{equation}

After that, since buffer queue is full, I/O server can not send more data to I/O buffer nodes, have to block any read and write request since that.
%\kento{Why ??}.

### 2014-07-01 paper/src/5-5_related_work.tex
0701

\section{Related Work}
\label{sec:related_work}
Cloud computing is becoming a topic of much interest in recent years, not only famous Internet companies like google, Amazon, IBM, Oracle, Microsoft provide public cloud, many companies start to build or have built private cloud for internal computation. Recently hybrid cloud, which is a composition of two or more clouds (private or public) is becoming a hot topic since it allows a business to take advantage of the scalability and cost-effectiveness that a public cloud offers without exposing critical application and data to third-party vulnerabilties, also by using cloud bursting, a small private cloud can easily burst into a large cloud to deal with temporality request peak. 
Several rearch works have been done on hybrid cloud and cloud bursting, Tekin Bicer \emph{el at.}\cite{time_and_cost} considered a software framework to enable data-intensive computing with cloud bursting, which use a combination of compute resources from local cluster and a public cloud to proceesing on a geographically distributed data set.
Their framework assume computation nodes allocated in both local cluster and public cloud, and data set is geographically distributed, However in our study, data set is stored in local system and in order to obtain a high communication throughput between computation nodes, we assume that nodes used for the same job allocated in the same system.
Another cloud bursting application can be seen in Tian Guo\emph{el at.}\cite{Seagull}, they introduced a system called Seagull, designed to facilitate cloud brusting by determining which applications should be transitioned into the cloud and automating the movement process at the proper time. Their work focused on determine which applications should be moved to public cloud, and our work focus on the methdology of filling the I/O throughput in cloud bursting.

There are also several paper about data I/O throughput, transfering and data processing in hybrid cloud.
Chiba Tatsuhiro \emph{el at.}\cite{Chiba} proposed two high performance multicast algorithms used for transfering large amounts of data stored in Amazon S3 to multiple Amazon EC2 nodes.
Tekin Bicer \emph{el at.}\cite{MATE-EC2} also described a middleware that allows the specification of data processing using a high-level API in Amazon S3.

>>>>

\section{Related Work}
\label{sec:related_work}
Cloud computing is becoming a topic of much interest in recent years, not only famous Internet companies like google, Amazon, IBM, Oracle, Microsoft provide public cloud, many companies start to build or have built private cloud for internal computation. Recently hybrid cloud, which is a composition of two or more clouds (private or public) is becoming a hot topic since it allows a business to take advantage of the scalability and cost-effectiveness that a public cloud offers without exposing critical application and data to third-party vulnerabilities, also by using cloud bursting, a small private cloud can easily burst into a large cloud to deal with temporarily request peak. 
Several research works have been done on hybrid cloud and cloud bursting, Tekin Bicer \emph{el at.}\cite{time_and_cost} considered a software framework to enable data-intensive computing with cloud bursting, which use a combination of compute resources from local cluster and a public cloud to processing on a geographically distributed data set.
Their framework assume computation nodes allocated in both local cluster and public cloud, and data set is geographically distributed, However in our study, data set is stored in local system and in order to obtain a high communication throughput between computation nodes, we assume that nodes used for the same job allocated in the same system.
Another cloud bursting application can be seen in Tian Guo\emph{el at.}\cite{Seagull}, they introduced a system called Seagull, designed to facilitate cloud bursting by determining which applications should be transitioned into the cloud and automating the movement process at the proper time. Their work focused on determine which applications should be moved to public cloud, and our work focus on the methodology of filling the I/O throughput in cloud bursting.

There are also several paper about data I/O throughput, transferring and data processing in hybrid cloud.
Chiba Tatsuhiro \emph{el at.}\cite{Chiba} proposed two high performance multicast algorithms used for transferring large amounts of data stored in Amazon S3 to multiple Amazon EC2 nodes.
Tekin Bicer \emph{el at.}\cite{MATE-EC2} also described a middleware that allows the specification of data processing using a high-level API in Amazon S3.

### 2014-07-01 paper/src/6_conclusion.tex
0701

From simulation result, we showed that our I/O burst buffer can burst I/O throughput about 4-20 times depends on cache hit rate as well as reduce overall cost about 2-12 times when Internet throughput is far smaller than interconnection throughput.

>>>>

From simulation result, we showed that our I/O burst buffer solution can burst I/O throughput about 4-20 times depends on cache hit rate as well as reduce overall cost about 2-12 times when Internet throughput is far smaller than interconnection throughput.
